---
title: "Homework 5"
author: "Shelby"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(classdata)
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
str(choco)
```


1. What is the overall number of chocolate bars rated?

There are 1852 observations, so there are 1852 chocolate bars that were rated. 


2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

The number of ratings increased from 2006 until 2015, dropped slightly in 2016, and fell much lower in 2017.

```{r}

choco$Review.Date <- as.factor(choco$Review.Date)
ggplot(choco, aes(x = Review.Date)) + geom_bar()
```


3.For each of the questions below provide at least one graphic as a basis for your answer.

  1.How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
  
The majority of ratings fall between 2.5 and 4.0. There appear to be outliers at 1.5.
  
```{r}

choco$Rating.factor <- as.factor(choco$Rating)
ggplot(choco, aes(x = Rating.factor)) + geom_bar()

```  
  
  2.Do ratings depend on the cocoa percentage of a chocolate bar?
  
  Ratings do not appear to depend on the cocoa percentage of a chocolate bar.
  
```{r}

ggplot(choco, aes(x = Rating, y = Cocoa.Pct)) +
  geom_point()
ggplot(choco, aes(x = Rating.factor, y = Cocoa.Pct)) +
  geom_boxplot()

```
  
  
  3.How do ratings compare across different company locations? Focus on the three locations with the most ratings:
  
```{r}
choco1 = choco
dplyr::filter(choco1, Company.Location %in% c("U.S.A.", "France", "Canada"))


ggplot(choco1, aes(x = Company.Location, fill=factor(Rating))) + geom_bar()


```

Hint:dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

Discuss a question (one for each group member) you want to investigate.

Shelby:

Greg:

Seana:

Answer this question by graphs.

Conclusions.

Paragraph discussing workflow
