---
title: "Homework 5"
author: "Shelby"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(classdata)
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
str(choco)
```


1. What is the overall number of chocolate bars rated?

There are 1852 rows, so excluding the title row there are 1851 chocolate bars that were rated. 


2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}
ggplot(choco, aes(x=Review.Date) + geom_boxplot() 
```


3.For each of the questions below provide at least one graphic as a basis for your answer.

  1.How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
  
  2.Do ratings depend on the cocoa percentage of a chocolate bar?
  
  3.How do ratings compare across different company locations? Focus on the three locations with the most ratings:
  
Hint:dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

Discuss a question (one for each group member) you want to investigate.

Shelby:

Greg:

Seana:

Answer this question by graphs.

Conclusions.

Paragraph discussing workflow
